---
title: "Picking a College Major"
author: "Damfello"
date: "12/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(scales)
theme_set(theme_light())
```

```{r}
recent_grads <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv")
```

```{r}
recent_grads %>% 
  ggplot(aes(Median)) +
  geom_histogram()
```
###Creating the object/container: majors_processed
```{r}
majors_processed <- recent_grads %>%
  arrange(desc(Median)) %>%
  mutate(Major = str_to_title(Major), ## To skip capital letters in texts from Categories
           Major = fct_reorder(Major, Median)) 
```

### Also aggregating by categories

```{r}
by_major_category <- majors_processed %>%
  filter(!is.na(Total)) %>%
  group_by(Major_category) %>%
  summarize(Men = sum(Men),
            Women = sum(Women),
            Total = sum(Total), 
            MedianSalary = sum(Median * Sample_size) / sum(Sample_size)) %>%
  mutate(ShareWomen = Women / Total) %>%
  arrange(desc(ShareWomen))

```


### Most commn Majors by Gender
```{r}
by_major_category %>%
   mutate(Major_category = fct_reorder(Major_category, Total)) %>%
  gather(Gender, Number, Men, Women) %>%
  ggplot(aes(Major_category, Number, fill = Gender)) +
geom_col() +
  scale_y_continuous(labels = comma_format()) +
  coord_flip() +
  labs(x = "",
       y = "Total # of Graduates", 
       title = "What are the most common Major Categories?")
```


### What categiories of Majors make more money than others?

```{r}
majors_processed %>%
  mutate(Major_category = fct_reorder(Major_category, Median)) %>%
  ggplot(aes(Major_category, Median, fill = Major_category)) +
  geom_boxplot() +
  scale_y_continuous(labels = dollar_format()) +
  expand_limits(y = 0) +
  coord_flip() +
  theme(legend.position = "none")

  #To compare a couple of distributions


```

### What are the highest earning majors?

```{r}
majors_processed <- recent_grads %>%
  arrange(desc(Median)) %>%
  select(Major, Major_category, Median, P25th, P75th, Sample_size) %>%
  mutate(Major = str_to_title(Major), ## To skip capital letters in texts from Categories
           Major = fct_reorder(Major, Median)) 

majors_processed %>%
  filter(Sample_size >= 100) %>%  ##Selecting the most common categories, or with more surveys answered
    head(20) %>%
  ggplot(aes(Major, Median, color = Major_category)) +
  geom_point() +
  geom_errorbar(aes(ymin = P25th, ymax = P75th)) +  ## To show intervals, using the columns P25th and P75th
  expand_limits(y = 0) +  ## To Y-axis start from Zero, because geom_point does not stat from Zero
   scale_y_continuous(labels = dollar_format()) + #To show Y data in $
  coord_flip() +
  labs(title = " What are the highest-earning majors?",
       subtitle = "Top 20 Majors with at least 100 graduates surveyed. Bars represent the 25th to 75th percentile", 
       x ="", ##To hide Label-Name of Majors in the graph, because obiously are the Majors
       y = "Median salary of graduates")
```
### What are the lowest earning Majors?
```{r}
majors_processed %>%
  filter(Sample_size >= 100) %>%
    tail(20) %>%
  ggplot(aes(Major, Median, color = Major_category)) +
  geom_point() +
  geom_errorbar(aes(ymin = P25th, ymax = P75th)) +  ## To show intervals, using the columns P25th and P75th
  expand_limits(y = 0) +  ## To Y-axis start from Zero, because geom_point does not stat from Zero
  coord_flip()
```
###Understanding the variation
```{r}
majors_processed %>%
  ggplot(aes(Sample_size, Median)) +
geom_point() +
geom_text(aes(label = Major), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10()
```

## How does gender breakdown relate to typical earnings?
```{r}
majors_processed %>%
  arrange(desc(Total)) %>%
  head(20) %>%
    mutate(Major = fct_reorder(Major, Total)) %>%
gather(Gender, Number, Men, Women) %>%
 ggplot(aes(Major, Number, fill = Gender)) +
  geom_col() +
  coord_flip()

```

```{r}
library(ggrepel)
by_major_category %>%
  mutate(Major_category = fct_lump(Major_category, 6)) %>%
  ggplot(aes(ShareWomen, MedianSalary, color = Major_category)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text_repel(aes(label = Major_category), force = .2) +
  expand_limits(y = 0)
  
```

```{r}
library(ggrepel)
library(plotly)
g <- majors_processed %>%
  mutate(Major_category = fct_lump(Major_category, 4)) %>%
  ggplot(aes(ShareWomen, Median, color = Major_category, size = Sample_size, label = Major)) +
  geom_point() +
  geom_smooth(aes(group = 1),method = "lm") +
  scale_x_continuous(labels = percent_format()) +
   scale_y_continuous(labels = dollar_format()) +
  expand_limits(y = 0)

ggplotly(g)
```
##Predict Median from ShareWomen, and if exist a significan effect.
### Sample_Size it's a weighting varaible. It means that for e.g. Metallurgical Engineering won't affect too much the prediction, because it's weight (Sample_Size) it's low: 3

```{r} 
majors_processed %>%
  select(Major, Total, ShareWomen, Sample_size, Median) %>%
  lm(Median ~ ShareWomen, data = ., weights = Sample_size) %>%
summary()
### A negative correlation exists. If ShareWomen went from zero to 100% women, the expected median salary would go down by -23650 
### refresh the theory about Linear Regression interpretation
```

```{r}
library(broom)

majors_processed %>%
  select(Major, Major_category, Total, ShareWomen, Sample_size, Median) %>%
  add_count(Major_category) %>%
  filter(n >= 10) %>%
  nest(-Major_category) %>%
  mutate(model = map(data, ~ lm(Median ~ ShareWomen, data = ., weights = Sample_size)),
         tidied = map(model, tidy)) %>%
  unnest(tidied) %>%
  filter(term == "ShareWomen") %>%
  arrange(estimate) %>%
  mutate(frd = p.adjust(p.value, method = "fdr"))

  
  
```
###First exploration of IQR 

```{r}
majors_processed %>%
  filter(Sample_size >= 100) %>%
  mutate(IQR = P75th - P25th) %>%
  arrange(desc(IQR)) %>%
  view()
```


### Future work 
1. Examing unemployment and fraction taking a job requiring 
2. Examing interquartile (IQR) ranges




```{r}

knitr::knit_exit()
```
### Draft work


### What were the most common majors? (Since there were 173, we're not going to show them all)
```{r}
majors_processed %>%
  mutate(Major = fct_reorder(Major, Total)) %>%
  arrange(desc(Total)) %>%
  head(20) %>%
  ggplot(aes(Major, Total, fill = Major_category)) +
geom_col() +
  coord_flip() +
  scale_y_continuous(labels = comma_format()) +
  labs(x = "",
       y = "Total # of Graduates")

```



## What are the Most common Majors?
### What major categories (e.g. engineering, psychology, business) were most common?

```{r}
majors_processed %>%
  count(Major_category, wt = Total, sort = TRUE) %>%
  mutate(Major_category = fct_reorder(Major_category, n)) %>%
  ggplot(aes(Major_category, n, fill = Major_category)) +
geom_col() +
  coord_flip() +
  labs(x = "",
       y = "Total # of Graduates")
theme(legend.position = "none")

```

### Another way to see the same information

```{r}
majors_processed %>%
  group_by(Major_category) %>%
  summarize(Median = median(Median)) %>%
  mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
   ggplot(aes(Major_category, Median)) +
  geom_col() +
  scale_y_continuous(labels = dollar_format()) + #To show Y data in $
    coord_flip()
  #To compare a couple of distributions
```